Literature Review - Informal

### 2019-12-22 Literature Review/Literature Review - Informal/sample.tex
added comments

@@

@@

@@

@@

\begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
towards ensuring that emergent phenomenon and swarm behaviour are as expected by the user. \item
Fault Detection in limited communication: Considering the ability of a swarm to, in a decentralised
approach, consider which robots in the team have failed, even in cases of no communication or
multiple failures. \end{itemize}

@@

\begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
SREs which have a limited or erroneous model. \item Agent Failures: The Dec-POMDP model uses a
centralised planner which acts offline. It therefore assumes that the agents will be able to carry
out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}

>>>>

\newcommand\fr[1]{\textcolor{red}{FR: #1}}

@@

\fr{Is 'Hard Coded' the terms also used in this literature, or is it your own?}

@@

\fr{What are the standard techniques used in swarms? that is, how are swarms and their interactions modelled? how are solutions computed? what kind of algorithms are used in this area? most importantly, does any of these overlap with any of the areas belos, for example (PO)MDPs?}

@@

\fr{Fault detection and fault recovery (D\&R) is one of the themes that encompasse several different research areas. As such, it would be interesting to check whether the techniques applied to Fault D\&R can be successfully exported from one area to another. However, this depends essentially on the different modelling assumptions.}

@@

\begin{itemize} \item Healing through co-evolution: The application of heterogenous robot swarms
towards ensuring that emergent phenomenon and swarm behaviour are as
expected by the user.

\item Fault Detection in limited communication:
Considering the ability of a swarm to, in a decentralised approach,
consider which robots in the team have failed, even in cases of no
communication or multiple failures.

\fr{The second item looks promising, possibly in combinations with
  techniques from Game Theory and MARL. Let's keep Fault R\&D in
  mind.}

\end{itemize}

@@

\begin{itemize} \item Significant Rare Events: Consider Dec-POMDP capability to remain robust to
  SREs which have a limited or erroneous model.

\item Agent Failures: The Dec-POMDP model uses a
centralised planner which acts offline. It therefore assumes that the agents will be able to carry
out their assigned tasks. It would be interesting to examine the possibility of, either adaptive
planning, or planning with contingencies in the Dec-POMDP framework. \end{itemize}

\fr{It looks like this second point is related to Fault R\&D discussed above. It might be worth to make a comparison and see what are the general results in the two areas.\\
Also, it might be interesting to understand why swarms scale up better
than MDPs, and in general why the former have better computational
properties than the latter: is it a matter of
``homogeneity''? Then, what about considering ``homogeneous'' MDPs, or
some other swarm-like restriction? It might be interesting to combine
the two approaches in order to get the ``best of both worlds''.}
